### 2013-09-18 chi2014/related.tex
Related work: nature of crowd market

%The nature of microtask marketplace also re.. .. identified high variance of turk eff

>>>>

The nature of microtask marketplace also calls for an alternative structure for brainstorming tasks in this setting. Researchers have found that 30\% or more submission on Mechanical Turk may be low quality \cite{kittur2008crowdsourcing}. For example, submissions to a brainstorming task for a company name are sometimes grammartically awkward or offensive \cite{little2010exploring}. These low quality responses were not found in walk-in brainstorming studies. Bernstein et al. identified high variance of effort Amazon Mechanical Turk workers put on task \cite{soylent}. They characterized two worker personas at opposite ends of the effort spectrum: the {\em Eager Beaver\/} who goes beyond task requirement and the {\em Lazy Turker\/} who does as little work as necessary to get paid. A brainstorming task that asks participants to generate as many ideas as they can under a set time limit might not be practical. A {\em Lazy Turker\/} can simply fill in a few ideas and wait for the time to run out instead of exerting full effort. This requirement does not map well with most previous work on brainstorming where the task are time-limited.
